Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-25 Paper/ms.tex
phase definition clarification

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: the orbital period $P_i$, the semi-amplitude (in metres
per second) of the RV signal $A_i$, the phase of the signal
$\phi_i$, the eccentricity $e_i$, and the ``viewing angle'' $\theta_i$.

>>>>

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: the orbital period $P_i$, the semi-amplitude (in metres
per second) of the RV signal $A_i$, the phase of the signal
$\phi_i$ (defined such that $\psi=0$ gives an RV signal whose maximum is at
$t=0$),
the eccentricity $e_i$, and the ``viewing angle'' $\theta_i$.
